QALY Comparisons - `r params$experiment` - `r params$intervention` - `r params$baseline`

### 2024-03-12 minos/outcomes/QALY_comparison2.Rmd
Fixed one final typo in QALY_comparison2.Rmd and added £75 interventions to the combined qaly_SCP run targets

```{r}
experiment <- params$experiment
baseline <- params$base
intervention <- params$intervention
#intervention2 <- params$intervention2
start.year <- params$start.year
# # 
# experiment <- 'glasgow_scaled'
# baseline <- 'baseline'
# ints <- c('50All', '50UniversalCredit')
# start.year <- 2020
```

>>>>

```{r}
experiment <- params$experiment
baseline <- params$base
ints <- params$intervention
#intervention2 <- params$intervention2
start.year <- params$start.year
# # 
# experiment <- 'glasgow_scaled'
# baseline <- 'baseline'
# ints <- c('50All', '50UniversalCredit')
# start.year <- 2020
```
